\textbf{The Mint Scale: A Fresh Validation of the Multimodal Interoception Questionnaire and Comparison to the MAIA, BPQ and IAS}

### 2025-07-02 paper/manuscript.qmd
add dim names

```{r}
#| label: fig-three
#| fig-cap: "Item loadings. The table shows each item of the Mint with its cluster centrality, which is the EGA equivalent (in terms of interpretation) of factor loadings. It also shows how each lower-level cluster is related to higher-order metaclusters."
#| fig-align: "center"
#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"

>>>>

```{r}
#| label: fig-three
#| fig-cap: "Item loadings. The table shows each item of the Mint with its cluster centrality, which is the EGA equivalent (in terms of interpretation) of factor loadings. It also shows how each lower-level cluster is related to higher-order metaclusters. The lower-level clusters are Expulsion Accuracy (ExAc), Relaxation Awareness (RelA), Sexual Arousal Sensitivity (SexS), Cardiorespiratory Confusion (CaCo), Urointestinal Inaccuracy (UrIn), Dermal Hypersensitivity (Derm), Satiety Noticing (Sati), Olfactory Compensation (Olfa), Respiroception (Resp), Cardioception (Card),  Gastroception (Gast)."
#| fig-align: "center"
#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
#| out-width: "100%"

### 2025-07-02 paper/manuscript.tex
add dim names

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Giulia
Poreiro}{0000-0002-2343-5109}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, leftrule=.75mm, toprule=.15mm, opacityback=0, breakable, colback=white, arc=.35mm, rightrule=.15mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm]

@@

{\caption{{Item loadings. The table shows each item of the Mint with its
cluster centrality, which is the EGA equivalent (in terms of
interpretation) of factor loadings. It also shows how each lower-level
cluster is related to higher-order metaclusters.}{\label{fig-three}}}}

>>>>

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Giulia
Poreiro}{0000-0002-2343-5109}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, breakable, colback=white, rightrule=.15mm, colframe=quarto-callout-note-color-frame, toprule=.15mm, bottomrule=.15mm, arc=.35mm, leftrule=.75mm, opacityback=0]

@@

{\caption{{Item loadings. The table shows each item of the Mint with its
cluster centrality, which is the EGA equivalent (in terms of
interpretation) of factor loadings. It also shows how each lower-level
cluster is related to higher-order metaclusters. The lower-level
clusters are Expulsion Accuracy (ExAc), Relaxation Awareness (RelA),
Sexual Arousal Sensitivity (SexS), Cardiorespiratory Confusion (CaCo),
Urointestinal Inaccuracy (UrIn), Dermal Hypersensitivity (Derm), Satiety
Noticing (Sati), Olfactory Compensation (Olfa), Respiroception (Resp),
Cardioception (Card), Gastroception (Gast).}{\label{fig-three}}}}
